Effects of pre-existing structures on the seismicity of the Charlevoix Seismic Zone

### 2019-06-27 Rebuttal_Letter.tex

The following are our detailed responses to the comments by the reviewers:

\Reviewer{\#1}

\begin{response}{The manuscript of Fadugba et al. "Effects of pre-existing structures on the seismicity of the Charlevoix Seismic Zone" introduces a modeling study assessing the stress perturbation due to a specific tectonic structure, that is, a rift system overprinted on the impact crater in Charlevoix Seismic Zone, eastern Canada. The effects of possible factors, including fault geometry, frictional strengths along faults, elastic properties of the crater and the different velocity models, are being discussed by comparing the causal stress perturbations to relocated seismic distributions. They study the combined effects of the impact zone and rift faults, confirm the importance of the two tectonic factors in explaining the stress perturbation, and provide a quantified estimation of the elastic contrast within and outside the impact crater. Overall, I find that their research approach is well designed. While the result is clearly presented, my main concern is how to justify conclusions based on model comparisons with single factor control.}
\end{response}

\begin{response}{I recommend the authors to justify the assumption of the independency effect of involved factors on stress perturbations, or that they have consistently monotonous effects.}
    The independency effect, if we understand it correctly, is not assumed but achieved by our experiment design, in which a reference model is compared with a model with only one parameter changed. We also believe our original results were already showing that that the controlled parameters have consistently monotonous effects. However, in this revision, we have run more models so that all the explored parameters have more regular intervals and thus the monotonicity of model responses can be exposed more clearly. For more details about the changes we have made in this regard, please refer to our response right below as well as those to the reviewer's specific comments.
\end{response}

@@

We have added Fig. S1 in the supplementary information.

\end{response}

\begin{response}{2. Line 116: Introduce the computational efficiency of your model, like how much cores your model requests, how long it takes. You can add this information into Table 1 if it varies much between different models.}

  We have added the computational efficiency of our model in the model geometry section (Lines 126-132) of the manuscript. We did not add the computational efficiency to Table 1 because it does not change significantly among the models except for the SD65R25 model, which took about twice longer to run for the same model time. We do not clearly understand why this model is particularly slow and further analyzing computational efficiency is beyond the scope of this paper.

@@

  %\add[EC]{, which took about twice longer to run for the same model time.} \annote[EC]{which may be due to the shallower fault dips.}{The shallower fault dips are the difference of SD65R25 from the others but does not directly explain why this model should take much less time. We can go ahead and speculate about possible reasons but it would be just enough to say that we do not clearly understand why this model is particularly slow and further analyzing computational efficiency is beyond the scope of this paper.}
  %\annote[EC]{except for the SD65R25 model}{This model then needs further explanation why it took a significantly longer or short time}. 
  %\note[EC]{Is there a reason why you did not follow the reviewer's suggestion to add this into to Table 1?}
\end{response}

\begin{response}{3. Line 131-133: I do not understand why you set your boundary conditions as the differential stress reaches 706 MPa. Do you set a criterion for shear stress somewhere else? Please make it more clear.}

  %\annote[EC]{We agree with the reviewer}{Agree only when you are sure that doing so would not negatively affect your arguments, assumptions or the overall integrity of your paper. Never confess; only justify.} on the high differential stress at seismogenic depth in our study, due to}
  The differential stress of 706 MPa at 10 km depth is based on Byerlee's law under the assumption of  
  %$\mu$ equal to 0.6 and \add[OF]{The equation of Byerlee's law has a μ value of 0.6. It is not an assumption in our study.}
  %\add[EC]{$\mu$ equal to 0.6 and} 
  the absence of pore-fluid pressure. The full derivation of this value is now provided in the supplementary information. Shear stress was not considered as a stopping criterion. In addition, we have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 530-540).

@@

\begin{response}{4. Section 2.3: You did not mention the values of bulk modulus and shear modulus applied in your calculation.}

  PyLith, the modeling software used in this study, internally converts P and S wave velocities and density to bulk and shear moduli. For readers' reference, however, we now list representative values of elastic moduli in Table 1. 
  %\add[EC]{For readers' reference, however, we now list representative values of elastic moduli in Table 1.}\note[EC]{Seun, please take care of this.}
\end{response}

\begin{response}{5. Line 154-156: As I said in the main concern, you need to justify the reduction of 10\% from the velocity model to represent the impact crater area, instead of, for example, 2\%, 5\%, or 20\%.}

  We ran extra models to have a series of models from 0 to 20 \% reduction. No significant changes in the model results were found in these models. The 10\% reduction in the density of corresponding crustal rock is to model a  damaged crustal rock (Lines 177-180). 
  %\annote[EC]{realistic}{Without further justification or proper citation of supporting evidence, you cannot say this. Support it or remove it.} 
  %{The main text should be accordingly revised. The point should be that, in all the presented models, the impact structure has elastic moduli reduced by 10 \% relative to the surrounding crust but the model results were insensitive to other amounts of reduction as see in Fig. S3 in the supplementary information.}
\end{response}

@@

\begin{response}{6. Line 164-165: According to Marone (1995), the assumption of zero cohesion could be valid for the pre-existing fractures sheared at low normal stress. In your models, the fault depth reaches up to 40 km (at least the stress change at 25 km depth is discussed), which is not the case for a low normal stress. It will be helpful to discuss the situation of faults with reasonable cohesive stress values, especially how this influence the fitting of friction coefficient.}

   % The faults in our models extend to 40 km but slips on them occur only down to about 10 km due to our stopping criterion. %{Correct this if I'm wrong.} 
   % Since the non-slipping portion of the faults are irrelevant, the condition of low normal stress is already being satisfied. For reference, however, we have explored non-zero values of cohesion and their impact on the results are shown in Fig. S4 in the supplementary information.

    We have explored non-zero values of cohesion and their impact on the results are shown in Fig. S4 in the supplementary information. However, low-cohesion results show a better spatial correlation with seismicity.

@@

\end{response}

\begin{response}{7. Line 226-231: When evaluate the modeling result, I suggest the authors to quantify the fitting between the simulated stress change and the earthquake hypocenters. It will help convincing the readers of preferred model parameters. For example, I do not see it necessarily to prefer the frictional coefficient equals to 0.3 over 0.4 based on Figure 11.}

   We have added a quantitative assessment
   %\annote[EC]{qualitative assessment}{Why is it still only qualitative? Have you tried one of the ideas I suggested? If none worked, you are supposed to let me know and look at another solution. Unless you have a good reason to ignore the reviewer's suggestion, the editor and the reviewer would be very curious why you didn't follow the suggestion. This is indeed the main reason why I asked if you had run into any trouble while revising the manuscript. Please take care of this and let me know if you need hlep.} \add[OF]{I am sorry it was a typo. I meant quantitative.}
   of the correlation between the change in differential stress and the observed seismicity by determining the percentage of hypocenters in the region with $\Delta\sigma_{D}^\prime \ge$ 0.5\% without accounting for uncertainty in hypocenter relocation (Line 199-203). We added a discussion on the choice of the friction coefficient in Lines 506-509.
    %: 1) the change in differential stress maps changes with fault geometry, and we have established an along-strike variation in the fault dips in this study; and 2) the 3D velocity model is very well defined in the upper 5 km depth which may introduced an uncertainty in the hypocenter relocation.
\end{response}

@@

\begin{response}{8. Line 312: You need to justify the mesh size of 4 km in Section 2.1.}

 % \annote[EC]{We have justified}{You cannot simply say like this. Do describe what is the justification here as well.} the mesh size in Section 2.1 
  We use a mesh size of 4 km to determine the effect of friction coefficient due to the expensive computation time of models with $\mu$ values of 0.1 and 0.2 (Lines 118-122).
\end{response}

@@

\begin{response}{An aspect that may have been missed is the fact that the epicentral map, such as Fig. 1, does not show a complete view of the regional seismicity. The SSW portion of the St. Lawrence River (upstream towards Quebec City) is also active (although not as much as the interior of the astrobleme). The dataset shown is the one of Powell and Lamontagne (2017) which was a selection of events based on their locations within the network of seismograph stations, but for this map view, I suggest that a more complete dataset is presented. The data can be downloaded from the earthquakescanada web site.}

  We have plotted the complete dataset in Fig. 1. We represented the relocated hypocenters of Powell and Lamontagne (2017) as circles and the other earthquakes that are not in the relocated catalog as diamonds.
\end{response}

\begin{response}{In a couple of places, authors use the expression 'large magnitude earthquakes'... Except for the 1925 M 6.2 earthquake, we are uncertain about the exact position of the 'large' earthquakes in Charlevoix (four other M6+; 1663; 1791, 1860,1870... although 1870 M 6.5 was probably near Ile-aux-Coudres). It would be better to say that the M4+ earthquakes, appear to occur more often in the NE portion of the CSZ. Stevens (1980) also found that some M4+ earthquakes of the period 1924-1980 also occurred at the SE end.}

  We have edited the manuscript accordingly (see Lines 447-449). We have also included the findings of Steven (1980) in our discussion.
\end{response}

@@

\begin{response}{The authors write that the focal mechanisms of the CSZ were not well defined. I disagree with them. You can check this OF report, which shows that the Quality 'A' mechanisms were well defined by the P first motions. I think that Mazzotti used most of them in his catalog.
https://geoscan.nrcan.gc.ca/starweb/geoscan/servlet.starweb?
path=geoscan/downloade.web\&search1=R=209378}

 The focal mechanisms are good, and we suggest that the focal mechanisms can be further constrained using waveform modeling to validate the magnitude of the stress rotation (Lines 563-565).
\end{response}

@@

\begin{response}{The model assumes an absence of pore-fluid pressure along faults. For this reason, the stress difference used by the authors is very high at seismogenic depth. It is my impression that worldwide, direct measurements and modelling of tectonic stresses suggest that the maximum crustal stress difference has an upper limit of about 100-200 MPa... very different from the 706 MPa suggested by the authors.
I think that the authors should discuss the possibility that high pore-fluid pressures exist at depth and their possible consequences. One aspect would be that faults could be reactivated at smaller angles from the maximum compressive stress and that the stress difference would have more realistic values.}

  The differential stress of 706MPa at 10 km depth is due to the assumption of the absence of pore-fluid pressure. The higher stopping criterion in our study is necessary to make faults slip at seismogenic depth under the assumption. We have included a discussion on the possibility and some consequences of pore-fluid pressure at depth (Lines 530-540).
\end{response}

### 2019-06-27 Supporting_Information.tex
Addressed comments

The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) for models with different impact structure-crust density ratio.  The maps show no significant change with density ratio. We use density ratio of 10\% in this study to model a realistic damaged crustal rock. 
\vspace{10mm} %5mm vertical space

@@

We compute $\Delta \sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ in a series of models in which the rift faults dip at 70$^{\circ}$ (i.e., SD70R25) but their cohesion ($C$) is varied systematically at a constant coefficient of friction ($\mu$) of 0.3. We assume that the fault parameters are the same for each rift fault and uniform throughout the fault surfaces. Six models with 0, 3, 5, 10, 20 and 30 MPa are constructed (Fig. \ref{S4}).

Magnitudes of $\Delta\sigma_D^{\prime}$ and $\phi_{\max}$ decrease with increasing cohesion. $\Delta\sigma_D^{\prime}$ maps spatially overlap with the distribution of seismicity at all the fault cohesions, especially well when the cohesion is less than 5 MPa (Fig. \ref{S4}A). However, the models could not explain some earthquakes in the SW corner of the crater. The $\Delta\sigma_D^{\prime}$ is not affected by a change in cohesion between 0 and 5 MPa. However, $\phi_{\max}$ approaches the reference no-fault model as the cohesion increases (Fig. \ref{S4}B). As cohesion increases, $\Delta\phi_{\max}$ decreases in value and the rotation is concentrated in the fault region outside the crater (Fig. \ref{S4}C). $\Delta\phi_{\max}$ is up to 10.8$^\circ$ when the cohesion is less than 5 MPa.

Figure \ref{S4} shows that $\mu$ is an essential fault parameter needed to explain the seismicity of the CSZ because the value of $\mu$ affects the slope of the Mohr-Coulomb failure envelope. We use a cohesion value of 0 MPa to explain the spatial distribution of observed seismicity in the CSZ.

@@

\begin{figure}[ht]
\setfigurenum{S4}
\includegraphics[width=25pc]{Figures/SD70R25C_S2.png}
\caption{Same as \ref{S3} but for the models with different cohesion values.}
\label{S4}
\end{figure}

The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) at various depths from the SD70R100 model.  $\Delta\sigma_{D}^{\prime}$ shows increased $\sigma_{D}$ relative to SNFR25 throughout the entire length of the rift faults at and below 15 km depth, hence the model predicts earthquakes in those regions.

\begin{figure}[ht]
\setfigurenum{S5}
\includegraphics[width=25pc]{Figures/SD70R100_S1.png}
\caption{Percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the SNFR25 at various depths depths from the SD70R100 model. Earthquakes within 2 km of each depth slice are represented by black dots in \ref{S3}A. Each figure is 70 $\times$ 70 km.}
\label{S5}
\end{figure}

@@

We test the response of the model results with different impact structure-crust moduli ratio. The model with a moduli ratio of 1.0 does not have the impact crater. The models show a better spatial correlation with the observed seismicity when the moduli ratio is 0.25.

@@

\begin{figure}[ht]
\setfigurenum{S6}
\includegraphics[width=25pc]{Figures/effect_of_moduli_ratio.png}
\caption{Same as \ref{S3} but for the models with different impact structure-crust moduli ratio.}
\label{S6}
\end{figure}

>>>>

The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) for models with different impact structure-crust density ratio (Fig. \ref{S3}).  The maps show no significant change with density ratio. We use density ratio of 10\% in this study to model a realistic damaged crustal rock. 
\vspace{10mm} %5mm vertical space

@@

The percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the reference model (SNFR25) at various depths from the SD70R100 model (Fig. \ref{S4}).  $\Delta\sigma_{D}^{\prime}$ shows increased $\sigma_{D}$ relative to SNFR25 throughout the entire length of the rift faults at and below 15 km depth, hence the model predicts earthquakes in those regions.

@@

\begin{figure}[ht]
\setfigurenum{S4}
\includegraphics[width=25pc]{Figures/SD70R100_S1.png}
\caption{Percentage change in differential stress ($\Delta\sigma_{D}^{\prime}$), SH$_{\max}$ orientation ($\phi_{\max}$), and the change in $\phi_{\max}$ ($\Delta\phi_{\max}$) relative to the SNFR25 at various depths depths from the SD70R100 model. Earthquakes within 2 km of each depth slice are represented by black dots in \ref{S3}A. Each figure is 70 $\times$ 70 km.}
\label{S4}
\end{figure}

@@

We test the response of the model results with different impact structure-crust moduli ratio (Fig. \ref{S5}). The model with a moduli ratio of 1.0 does not have the impact crater. The models show a better spatial correlation with the observed seismicity when the moduli ratio is 0.25.

@@

\begin{figure}[ht]
\setfigurenum{S5}
\includegraphics[width=25pc]{Figures/effect_of_moduli_ratio.png}
\caption{Same as \ref{S3} but for the models with different impact structure-crust moduli ratio.}
\label{S5}
\end{figure}

We compute $\Delta \sigma_{D}^{\prime}$, $\phi_{\max}$ and $\Delta \phi_{\max}^{\prime}$ in a series of models in which the rift faults dip at 70$^{\circ}$ (i.e., SD70R25) but their cohesion ($C$) is varied systematically at a constant coefficient of friction ($\mu$) of 0.3. We assume that the fault parameters are the same for each rift fault and uniform throughout the fault surfaces. Six models with 0, 3, 5, 10, 20 and 30 MPa are constructed (Fig. \ref{S6}).

Magnitudes of $\Delta\sigma_D^{\prime}$ and $\phi_{\max}$ decrease with increasing cohesion. $\Delta\sigma_D^{\prime}$ maps spatially overlap with the distribution of seismicity at all the fault cohesions, especially well when the cohesion is less than 5 MPa (Fig. \ref{S6}A). However, the models could not explain some earthquakes in the SW corner of the crater. The $\Delta\sigma_D^{\prime}$ is not affected by a change in cohesion between 0 and 5 MPa. However, $\phi_{\max}$ approaches the reference no-fault model as the cohesion increases (Fig. \ref{S6}B). As cohesion increases, $\Delta\phi_{\max}$ decreases in value and the rotation is concentrated in the fault region outside the crater (Fig. \ref{S6}C). $\Delta\phi_{\max}$ is up to 10.8$^\circ$ when the cohesion is less than 5 MPa.

Figure \ref{S6} shows that $\mu$ is an essential fault parameter needed to explain the seismicity of the CSZ because the value of $\mu$ affects the slope of the Mohr-Coulomb failure envelope. We use a cohesion value of 0 MPa to explain the spatial distribution of observed seismicity in the CSZ.

\begin{figure}[ht]
\setfigurenum{S6}
\includegraphics[width=25pc]{Figures/SD70R25C_S2.png}
\caption{Same as \ref{S3} but for the models with different cohesion values.}
\label{S6}
\end{figure}

### 2019-06-27 main_full_manuscript.tex
Addressed comments

Velocities are prescribed on the sides perpendicular to the $x$-axis (Fig. \ref{figtwo}A) while the $y$-perpendicular sides and the bottom boundary are free-slip and the top boundary is traction-free. Rather than applying velocities oblique to the sides, we rotate the model domain such that the $x$-axis is oriented to N55$^\circ$E, the regional SH$_{\max}$ direction~\citep{Zoback_1992} (Fig. \ref{figtwo}B). We apply a 1 m/yr compressive velocity in the x-axis direction. The magnitude of boundary velocity does not represent any tectonic loading in the continental interiors but has the sole purpose of increasing the differential stress ($\sigma_D$ = $\sigma_1 - \sigma_3$). Noting that \change[OF]{most earthquakes in the crater occur near 10 km depth}{the distribution of earthquakes within the impact structure has a peak at 10 km} \citep{Baird_2010,Powell_2017}, we increase the boundary displacement until $\sigma_D$ reaches 706 MPa at 10 km depth based on Byerlee's law for dry rocks, $\tau$  = 50 MPa + 0.6$\,\sigma_n$~\citep{Byerlee_1978}. \add[OF]{Supplementary Information provides more details of the full derivation of the stopping criterion for boundary loading. We assume that} $\sigma_3$ corresponds to the lithostatic stress \change[OF]{. C}{and adopt the sign convention that ompressive stress is negative.}

@@

\subsection{Treatment of rift faults}
We treat the rift faults as cohesive-frictional planes, on which slip vectors are not prescribed but determined by the model. In order to create relative motions across the rift fault planes, PyLith decouples the motion of the two sides of the faults by inserting cohesive cells on the fault surfaces. We assign a coefficient of static friction ($\mu$) and the cohesion ($C$) on the fault. We assume that $\mu$ and $C$ are uniform on the fault planes in each model but investigate the consequences of varying $\mu$ from 0.1 to 0.6 at a constant $C$ of 0 MPa. \add[OF]{We choose zero cohesion because it is appropriate for pre-existing faults with low normal stress}~\citep{Marone_Chris} \add[OF]{and slips on the model faults occur only down to about 10 km depth satisfying this condition.} \note[EC]{I think the following sentences should be in discussion, not here.}\add[OF]{We ran a series of models in which the rift faults dip at 70$^{\circ}$ and the friction coefficient ($\mu$) is fixed to be 0.3 while cohesion ($C$) is one of 0, 3, 5, 10, 20 and 30 MPa (Fig. S4). Cohesion values less than 5 MPa could explain the spatial distribution of observed seismicity in the CSZ.}

@@

\begin{table}
\caption{List of numerical models \note[EC]{Each symbol needs a description. Cohesion needs a unit. I gave a try with the $\dagger$ symbol.}}
\centering
\begin{tabular}{llcccccc}
\hline
Model & Velocity Model & Dip of Rift Faults & Moduli ratio & $\mu^{\dagger}$ & $C^{\dagger}$ & K$^{\dagger,*}$ (MPa) & G$^{\dagger,*}$ (MPa) \\
\hline
SNFR25  & Saguenay Region$^{1}$ & No faults & 0.25 & 0.3 & 0 & 55.7 & 32.7  \\
SD70R25  &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.3 & 0 & 55.7 & 32.7 \\
SD70R25V  &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.1-0.6 & 0 & 55.7 & 32.7 \\
%SD70R25M1 &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.1 & 0 \\
SD65R25  &  & $65^\circ-40^\circ-40^\circ$  & 0.25 & 0.3 & 0 & 55.7 & 32.7\\
SD70R50  &  & $70^\circ-70^\circ-70^\circ$  & 0.5 & 0.3 & 0 & 55.7 & 32.7 \\
SD70R100   &  & $70^\circ-70^\circ-70^\circ$  & 1.0 & 0.3 & 0 & 55.7 & 32.7 \\
LD70R25 & 1-D Model$^{2}$ & $70^\circ-70^\circ-70^\circ$ & 0.25 & 0.3  & 0 & 60.0 & 35.7 \\
TD70 & Tomography$^{3}$ & $70^\circ-70^\circ-70^\circ$ & - & 0.3 & 0 & 58.7 & 35.3 \\
\hline
\multicolumn{8}{l}{$^{1}$\citet{Somerville1990}. $^{2}$\citet{lamontagne1999}. $^{3}$\citet{Powell_2017}.$^{*}$K, G at 10 km depth.} \\
\multicolumn{8}{l}{$^{\dagger}$$\mu$, $C$, $K$ and $G$ are friction coefficient, cohesion, bulk and shear modulus, respectively.}

@@

The region of increased differential stress in SD65R25 exhibits well-defined linear trends near the rift faults, and thus gives a better explanation for the narrow and well-defined seismicity near the \change[OF]{crater}{impact structure} \note[EC]{Why do you say ``even though''? Does the percentage betray your or a general expectation?} \add[OF]{, even though the overall percentage of the hypocenters that fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% is about 25\%.} (Fig. \ref{fig:profiles_65_40_40_2km}). The SD65R25 model shows a region of negative $\Delta\sigma_{D}^{\prime}$ between the observed seismicity on the northernmost and southernmost faults. The earthquakes on the middle rift fault and most of the earthquakes on the southernmost fault outside the \change[OF]{crater}{impact structure} fall in regions with negative $\Delta\sigma_{D}^{\prime}$ (Fig. \ref{fig:profiles_65_40_40_2km}).

@@

Positive $\Delta\sigma_{D}^{\prime}$ values in SD70R100 are seen only at a depth of 10 km and their distribution does not fit the observed seismicity (Fig. \ref{fig:eff_of_moduli_ratio}B).  \add[OF]{About 23\% of the hypocenters fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} $\Delta\sigma_{D}^{\prime}$ correlates with observed seismicity below 15 km except for some earthquakes in the northern cluster. However, the model predicts earthquakes throughout the entire length of the rift faults at and below 15 km depth. Figures that shows all the depth slices are in the supplementary materials (Fig. S5). \add[OF]{The result of a model with an intermediate moduli ratio of 0.75 is somewhat between the SD70R50 and SD70R100 models (Fig. S6).}

@@

\subsection{Frictional strengths of the rift faults}
The surface expression of the rift faults used in this study correspond to the Gouffre Northwest Fault, Saint-Laurent fault and Charlevoix Fault (Fig. 1). We did not consider the South Shore fault given its aseismic nature and \change[OF]{its location at the extreme eastern edge of the crater}{it appears to mark a boundary to the active zone}~\citep{lamontagne1999}. Our models show that a $\mu$ of 0.3 and cohesion values of 0 MPa create $\Delta\sigma_{D}^\prime$ maps that spatially correlate with the seismicity of CSZ and the observed stress rotations (Fig. \ref{fig:eff_of_mu}). \add[OF]{A $\mu$ of 0.4 could also be suitable for the rift faults as the $\Delta\sigma_{D}^\prime$ maps also spatially correlate with the seismicity of CSZ, and some earthquakes also occurred at the SW region outside the impact structure (Fig. $\ref{figone}$). However, previous works in the CSZ agreed with a finite extent of the seismic zone} ~\citep[e.g.,][]{Stevens1980}. \change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig. \ref{figone}).

>>>>

Velocities are prescribed on the sides perpendicular to the $x$-axis (Fig. \ref{figtwo}A) while the $y$-perpendicular sides and the bottom boundary are free-slip and the top boundary is traction-free. Rather than applying velocities oblique to the sides, we rotate the model domain such that the $x$-axis is oriented to N55$^\circ$E, the regional SH$_{\max}$ direction~\citep{Zoback_1992} (Fig. \ref{figtwo}B). We apply a 1 m/yr compressive velocity in the x-axis direction. The magnitude of boundary velocity does not represent any tectonic loading in the continental interiors but has the sole purpose of increasing the differential stress ($\sigma_D$ = $\sigma_1 - \sigma_3$). Noting that \change[OF]{most earthquakes in the crater occur near 10 km depth}{the distribution of earthquakes within the impact structure has a peak at 10 km} \citep{Baird_2010,Powell_2017}, we increase the boundary displacement until $\sigma_D$ reaches 706 MPa at 10 km depth based on Byerlee's law for dry rocks, $\tau$  = 50 MPa + 0.6$\,\sigma_n$~\citep{Byerlee_1978}. \add[OF]{Supplementary Information provides more details of the full derivation of the stopping criterion for boundary loading. We assume that} $\sigma_3$ corresponds to the lithostatic stress \change[OF]{. C}{and adopt the sign convention that compressive stress is negative.}

@@

\subsection{Treatment of rift faults}
We treat the rift faults as cohesive-frictional planes, on which slip vectors are not prescribed but determined by the model. In order to create relative motions across the rift fault planes, PyLith decouples the motion of the two sides of the faults by inserting cohesive cells on the fault surfaces. We assign a coefficient of static friction ($\mu$) and the cohesion ($C$) on the fault. We assume that $\mu$ and $C$ are uniform on the fault planes in each model but investigate the consequences of varying $\mu$ from 0.1 to 0.6 at a constant $C$ of 0 MPa. \add[OF]{We choose zero cohesion because it is appropriate for pre-existing faults with low normal stress}~\citep{Marone_Chris}. 
%\add[OF]{and slips on the model faults occur only down to about 10 km depth satisfying this condition.} 
%\note[EC]{I think the following sentences should be in discussion, not here.}\add[OF]{We ran a series of models in which the rift faults dip at 70$^{\circ}$ and the friction coefficient ($\mu$) is fixed to be 0.3 while cohesion ($C$) is one of 0, 3, 5, 10, 20 and 30 MPa (Fig. S4). Cohesion values less than 5 MPa could explain the spatial distribution of observed seismicity in the CSZ.}

@@

\begin{table}
\caption{List of numerical models} 
%\note[EC]{Each symbol needs a description. Cohesion needs a unit. I gave a try with the $\dagger$ symbol.}}
\centering
\begin{tabular}{llcccccc}
\hline
Model & Velocity Model & Dip of Rift Faults & Moduli ratio & $\mu^{\dagger}$ & $C^{\dagger}$ (MPa) & K$^{\dagger,*}$ (MPa) & G$^{\dagger,*}$ (MPa) \\
\hline
SNFR25  & Saguenay Region$^{1}$ & No faults & 0.25 & 0.3 & 0 & 55.7 & 32.7  \\
SD70R25  &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.3 & 0 & 55.7 & 32.7 \\
SD70R25V  &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.1-0.6 & 0 & 55.7 & 32.7 \\
%SD70R25M1 &  & $70^\circ-70^\circ-70^\circ$  & 0.25 & 0.1 & 0 \\
SD65R25  &  & $65^\circ-40^\circ-40^\circ$  & 0.25 & 0.3 & 0 & 55.7 & 32.7\\
SD70R50  &  & $70^\circ-70^\circ-70^\circ$  & 0.5 & 0.3 & 0 & 55.7 & 32.7 \\
SD70R100   &  & $70^\circ-70^\circ-70^\circ$  & 1.0 & 0.3 & 0 & 55.7 & 32.7 \\
LD70R25 & 1-D Model$^{2}$ & $70^\circ-70^\circ-70^\circ$ & 0.25 & 0.3  & 0 & 60.0 & 35.7 \\
TD70 & Tomography$^{3}$ & $70^\circ-70^\circ-70^\circ$ & - & 0.3 & 0 & 58.7 & 35.3 \\
\hline
\multicolumn{8}{l}{$^{1}$\citet{Somerville1990}. $^{2}$\citet{lamontagne1999}. $^{3}$\citet{Powell_2017}.$^{*}$K, G at 10 km depth.} \\
\multicolumn{8}{l}{$^{\dagger}$$\mu$, $C$, $K$ and $G$ are friction coefficient, cohesion, bulk and shear modulus, respectively.}

@@

The region of increased differential stress in SD65R25 exhibits well-defined linear trends near the rift faults, and thus gives a better explanation for the narrow and well-defined seismicity near the \change[OF]{crater}{impact structure} (Fig. \ref{fig:profiles_65_40_40_2km}). \add[OF]{About 25\% of the hypocenters fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.}. The SD65R25 model shows a region of negative $\Delta\sigma_{D}^{\prime}$ between the observed seismicity on the northernmost and southernmost faults. The earthquakes on the middle rift fault and most of the earthquakes on the southernmost fault outside the \change[OF]{crater}{impact structure} fall in regions with negative $\Delta\sigma_{D}^{\prime}$ (Fig. \ref{fig:profiles_65_40_40_2km}).

%\note[EC]{Why do you say ``even though''? Does the percentage betray your or a general expectation?} \add[OF]{, even though the overall percentage of the hypocenters that fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\% is about 25\%.}

@@

Positive $\Delta\sigma_{D}^{\prime}$ values in SD70R100 are seen only at a depth of 10 km and their distribution does not fit the observed seismicity (Fig. \ref{fig:eff_of_moduli_ratio}B).  \add[OF]{About 23\% of the hypocenters fall in region with $\Delta\sigma_{D}^{\prime} \ge$ 0.5\%.} $\Delta\sigma_{D}^{\prime}$ correlates with observed seismicity below 15 km except for some earthquakes in the northern cluster. However, the model predicts earthquakes throughout the entire length of the rift faults at and below 15 km depth. Figures that shows all the depth slices are in the supplementary materials (Fig. S4). \add[OF]{The result of a model with an intermediate moduli ratio of 0.75 is somewhat between the SD70R50 and SD70R100 models (Fig. S5).}

@@

\subsection{Frictional strengths of the rift faults}
The surface expression of the rift faults used in this study correspond to the Gouffre Northwest Fault, Saint-Laurent fault and Charlevoix Fault (Fig. 1). We did not consider the South Shore fault given its aseismic nature and \change[OF]{its location at the extreme eastern edge of the crater}{it appears to mark a boundary to the active zone}~\citep{lamontagne1999}. Our models show that a $\mu$ of 0.3 and cohesion values of 0 MPa create $\Delta\sigma_{D}^\prime$ maps that spatially correlate with the seismicity of CSZ and the observed stress rotations (Fig. \ref{fig:eff_of_mu}). \add[OF]{We ran a series of models in which the rift faults dip at 70$^{\circ}$ and the friction coefficient ($\mu$) is fixed to be 0.3 while cohesion ($C$) is one of 0, 3, 5, 10, 20 and 30 MPa (Fig. S6). Cohesion values less than 5 MPa could explain the spatial distribution of observed seismicity in the CSZ.} \add[OF]{A $\mu$ of 0.4 could also be suitable for the rift faults as the $\Delta\sigma_{D}^\prime$ maps also spatially correlate with the seismicity of CSZ, and some earthquakes also occurred at the SW region outside the impact structure (Fig. $\ref{figone}$). However, previous works in the CSZ agreed with a finite extent of the seismic zone} ~\citep[e.g.,][]{Stevens1980}. \change[OF]{This}{Our fault model} is different from the work of \citet{Baird_2010} who modeled the Gouffre Northwest Fault, Saint-Laurent fault and South Shore Fault (Fig. \ref{figone}).
